Sharing statistics for SPARQL Federation optimization, with emphasis on benchmark quality

### 2012-01-12 eswc-2012/phdsymp.tex
texism
git-svn-id: https://svn.ifi.uio.no/repos/users/kjekje-phd@73 43ef1190-90fd-4dd7-a769-d0121f02b80e

\title{Sharing statistics for SPARQL Federation optimization, with
  emphasis on benchmark quality}
\author{Kjetil Kjernsmo}
\institute{Department of Informatics,
Postboks 1080 Blindern,
0316 Oslo, Norway}

@@

\maketitle
\email{kjekje@ifi.uio.no}

@@

This part of the thesis seeks to use advances from statistical
experimental planning to improve accuracy and dependability of
benchmarking. Already in 1926, Ronald~Fischer noted that complex
experiments can be much more efficient than simple
ones~\cite{Fisher_1926}\footnote{Cited in
  http://en.wikipedia.org/wiki/Factorial\_experiment}, starting the
experimental design field. One of the simpler designs is ``fractional
factorial design'', in which several ``factors'' are studied by using
different ``treatments''. In terms of SPARQL execution, one factor can
for example be the level of nested \texttt{OPTIONAL}s, number of
triples in a basic graph pattern, etc, and the treatment is to vary
these numbers. The key to understanding why this can be efficient is
that these variations need not occur in the same experiment. Thus,
many combinations of factors can be studied by carefully designing
queries to cover different factors, and a formalism called
``resolution'' has been developed to classify how well this has been
achieved.

@@

\bibliographystyle{plain}
\bibliography{selectivity,federation,benchmarks,statistics,optimization}

>>>>

\title{Sharing statistics for SPARQL Federation optimization, with
  emphasis on benchmark quality}
\titlerunning{Sharing statistics and benchmarking for SPARQL federation}
\author{Kjetil Kjernsmo\inst{1}}
\institute{Department of Informatics,
Postboks 1080 Blindern,
0316 Oslo, Norway
\email{kjekje@ifi.uio.no}}

@@

\maketitle

@@

This part of the thesis seeks to use advances from statistical
experimental planning to improve accuracy and dependability of
benchmarking. Already in 1926, Ronald~Fischer noted that complex
experiments can be much more efficient than simple
ones\footnote{Cited in
  http://en.wikipedia.org/wiki/Factorial\_experiment}, starting the
experimental design field. One of the simpler designs is ``fractional
factorial design'', in which several ``factors'' are studied by using
different ``treatments''. In terms of SPARQL execution, one factor can
for example be the level of nested \texttt{OPTIONAL}s, number of
triples in a basic graph pattern, etc, and the treatment is to vary
these numbers. The key to understanding why this can be efficient is
that these variations need not occur in the same experiment. Thus,
many combinations of factors can be studied by carefully designing
queries to cover different factors, and a formalism called
``resolution'' has been developed to classify how well this has been
achieved.

@@

\bibliographystyle{plain}
\bibliography{selectivity,federation,benchmarks,optimization}
